---
title: "One full iteration with tagmodr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{One full iteration with tagmodr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette walks one full iteration of the two-pass workflow on the
package's synthetic fixture. The fixture is a small "book club discussion"
dataset with two documents, seven tags (mixing ASCII and Japanese segments),
and twelve `highlight_tags` rows.

## Load the SQLite export

```{r}
library(tagmodr)

fixture <- system.file("extdata", "example_project.sqlite3", package = "tagmodr")
sqlite <- read_taguette_sqlite(fixture)
names(sqlite)
```

`read_taguette_sqlite()` returns a named list keyed by SQLite table name.
The three tables the pipeline cares about are `tags`, `highlight_tags`, and
`highlights` — see the README for how these column-shaped like/unlike their
names suggest.

## Review pass — materialise the hierarchy

Normalise tag paths so both ASCII and Japanese segment boundaries carry the
canonical `\\ ` separator, then build the per-highlight review table:

```{r}
tags_normalised <- normalize_tag_paths(sqlite$tags)
tags_normalised$path

review <- build_review_table(
  df.tag_table  = tags_normalised,
  df.highlights = sqlite$highlight_tags,
  df.snippets   = sqlite$highlights
)
head(review)
```

Notice that `normalize_tag_paths()` has inserted the space after `\\` in the
Japanese paths that were stored without it (`登場人物\\内面` →
`登場人物\\ 内面`).

In a real iteration, you would now write `review` to CSV, open it in Excel,
add the `Old_New` and `from_to` columns to describe your operations, and
save the workbook as `..mod.xlsx`. In this vignette we skip the Excel
round-trip and build the operations list directly.

## Mod pass — construct operations in memory

For demonstration, three operations:

1. Merge `Character\\ Grief` into `Style\\ Voice`.
2. Add a new tag `Character\\ Silence` and attach it to highlight 3.
3. Unlink `(highlight_id = 8, tag_id = 5)`.

```{r}
op_merge <- structure(
  list(
    str_from = "Character\\\\ Grief",
    str_to   = "Style\\\\ Voice"
  ),
  class = c("path_change", "list")
)
op_add <- structure(
  list(
    path = "Character\\\\ Silence",
    highlight_ids = 3L
  ),
  class = c("add", "list")
)
op_unlink <- structure(
  list(
    highlight_ids = 8L,
    tag_ids = 5L
  ),
  class = c("unlink", "list")
)
ops <- list("1" = op_merge, "2" = op_add, "3" = op_unlink)
```

Apply them:

```{r}
state <- apply_tagmod_ops(
  ops,
  df.tag_table  = tags_normalised,
  df.highlights = sqlite$highlight_tags
)

# tags after: the merged-from row is DEMOTED_, the new Silence tag has a fresh id.
state[[1]][, c("id", "path")]

# highlight_tags after: (8,5) is gone; the new tag has picked up (3, new_id).
tail(state[[2]])
```

## Write the updated SQLite

Splice the updated frames back into the list and write:

```{r}
sqlite$tags           <- state[[1]]
sqlite$highlight_tags <- state[[2]]

out <- tempfile(fileext = ".sqlite3")
write_taguette_sqlite(sqlite, out)
file.exists(out)
```

The written SQLite has the same table shape as the input and can be
re-imported into Taguette to see the reorganised codebook.

## In a real project

Instead of constructing `ops` in memory, you'd:

1. `readr::write_excel_csv(review, "project_tag_review.csv")`.
2. Open in Excel, save as `project_tag_review..mod.xlsx`, annotate.
3. `ops <- create_tagmod_list("project_tag_review..mod.xlsx", length.path = 4L)`.

The rest of the mod pass is identical.
